Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-01 overleaf/results.tex
evaluation section nuking references to biometric_fast
comment update

\ishaq{We don't have space to show individual benchmark graphs, and vec data is only plotted in individual benchmark graphs, so specifying what we use for vec experiment in the following text is unnecessary. (unless, we change the graph)}

@@

\ishaq{TODO: add a large table for LAN, incorporating as much data as possible}

@@

    \item {\em Biometric Matching (Fast)} is the faster instantiation taken from \cite{Demmler:2015}. Parameters are same as above.

>>>>

\ishaq{@Ana: I don't know what to do about this: In the following list of benchmarks, I specify paramters for vectorized experiments too. but we don't have enough space to show the vectorized only experiments (we could replace the graphs). Not sure if I should take it out}

@@

@@

    % \item {\em Biometric Matching (Fast)} is the faster instantiation taken from \cite{Demmler:2015}. Parameters are same as above.
